Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON, and the ERA5 and MERRA-2 reanalyses

### 2024-12-10 manuscript_agu.tex
Fixing stuff

\begin{keypoints}
\item Ground-based lidar evaluation of a km-scale global climate model and reanalyses reveals substantial cloud biases over the Southern Ocean.
\item Fog or low cloud is underestimated in the reanalyses. In all models a cloud occurrence peak at 500 m tends to be overestimated and too high.
\item A "too few, too bright" problem of underestimated cloud fraction, compensated by overestimated cloud albedo is present in the reanalyses.
\end{keypoints}

@@

SO radiation biases have been relatively large and systematic compared to the rest of the globe since at least CMIP3 \citeA{trenberth2010}, and the SO SW cloud radiative effect (CRE) bias is still positive in eight analyzed CMIP6 models analyzed by \citeA{schuddeboom2021} over the high-latitude SO, whereas over the low-latitude SO it tends to be more neutral or negative in some models. Too much absorbed SW radiation over the SO was also identified in the GSRM SCREAM \citeA{caldwell2021}. Compensating biases are possible, such as the `too few too bright' cloud bias, characterized by too small cloud fraction and too large cloud albedo \citeA{wall2017,kuma2020}, previously described by \citeA{webb2001}, \citeA{weare2004}, \citeA{zhang2005}, \citeA{karlsson2008}, \citeA{nam2012}, \citeA{klein2013}, and \citeA{bender2017} in other regions and models, which means that a model can maintain a reasonable SW radiation balance by reflecting too much SW radiation from clouds, but these cover too small an area. A study by \citeA{konsta2022} showed that this type of bias is still present in six analyzed CMIP6 models in tropical marine clouds, using the GCM-Oriented Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observation (CALIPSO) Cloud Product [CALIPSO--GOCCP; \citeA{chepfer2010}] and Polarization \& Anisotropy of Reflectances for Atmospheric Sciences coupled with Observations from a Lidar [PARASOL; \citeA{lier2008}] as a reference. They suggest improper simulation of subgrid-scale cloud heterogeneity as a cause. Compensating cloud biases in the Australian Community Climate and Earth System Simulator (ACCESS) – Atmosphere-only model version 2 (AM2) over the SO were analyzed by \citeA{fiddes2022} and \citeA{fiddes2024}. \citeA{possner2022} showed that over the SO, the DYAMOND GSRM ICON underestimates low-level cloud fraction on the order of 30\% [relative to Moderate Resolution Imaging Spectroradiometer (MODIS) data] and overestimates downwelling TOA SW radiation by approximately 10 Wm$^\mathrm{-2}$ [relative to the Clouds and the Earth’s Radiant Energy System (CERES) data] in the highest model resolution run (2.5 km). \citeA{zhao2022} reported a similar SW radiation bias in five analyzed CMIP6 models over high-latitude SO and the total cloud fraction underestimation on the order of 10\% over the entire 40--60°S SO. Recently, \citeA{ramadoss2024} analyzed 48 hours of km-scale ICON limited-area model NWP simulations over a SO region adjacent to Tasmania against the Clouds, Aerosols, Precipitation, Radiation, and atmospherIc Composition Over the southeRn oceaN (CAPRICORN) voyage cloud and precipitation observations \citeA{mcfarquhar2021}. They found the ICON cloud optical thickness was underestimated relative to Himawari‐8 satellite observations but also identified large differences in cloud top phase.

@@

\begin{figure}[b!]
\centering
\includegraphics[width=\textwidth]{img/ann.pdf}
\caption{
Artificial neural network (ANN) for prediction of precipitation in lidar backscatter. \textbf{(a)} Diagram showing the TensorFlow structure of the ANN, \textbf{(b)} randomly selected example samples of near-surface backscatter in four categories (clear, fog, rain, and snow), as determined by coincident human-performed weather observations, \textbf{(c)} receiver operating characteristic diagram of the ANN, \textbf{(d)} examples of 10-day time series of human-observed (`HUM') and predicted precipitation based on an ANN trained on all voyages (`ANN') and all voyages except for the shown voyage (`ANN2') during three randomly selected voyages with the available data. Here, by `randomly selected', we mean selected from the top of a permutation generated by a pseudo-random number generator to prevent authors' bias in the selection.
}
\label{fig:ann}
\end{figure}

>>>>

\begin{keypoints}
\item Ground-based lidar evaluation of a km-scale global climate model and reanalyses reveals substantial cloud biases over the Southern Ocean.
\item Fog or low cloud is underestimated in the reanalyses. In all models, a cloud peak at 500 m tends to be overestimated and too high.
\item A ``too few, too bright'' problem of underestimated cloud fraction, compensated by overestimated cloud albedo, is present in the reanalyses.
\end{keypoints}

@@

SO radiation biases have been relatively large and systematic compared to the rest of the globe since at least CMIP3 \citeA{trenberth2010}, and the SO SW cloud radiative effect (CRE) bias is still positive in eight analyzed CMIP6 models analyzed by \citeA{schuddeboom2021} over the high-latitude SO, whereas over the low-latitude SO it tends to be more neutral or negative in some models. Too much absorbed SW radiation over the SO was also identified in the GSRM SCREAM \citeA{caldwell2021}. Compensating biases are possible, such as the ``too few too bright'' cloud bias, characterized by too small cloud fraction and too large cloud albedo \citeA{wall2017,kuma2020}, previously described by \citeA{webb2001}, \citeA{weare2004}, \citeA{zhang2005}, \citeA{karlsson2008}, \citeA{nam2012}, \citeA{klein2013}, and \citeA{bender2017} in other regions and models, which means that a model can maintain a reasonable SW radiation balance by reflecting too much SW radiation from clouds, but these cover too small an area. A study by \citeA{konsta2022} showed that this type of bias is still present in six analyzed CMIP6 models in tropical marine clouds, using the GCM-Oriented Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observation (CALIPSO) Cloud Product [CALIPSO--GOCCP; \citeA{chepfer2010}] and Polarization \& Anisotropy of Reflectances for Atmospheric Sciences coupled with Observations from a Lidar [PARASOL; \citeA{lier2008}] as a reference. They suggest improper simulation of subgrid-scale cloud heterogeneity as a cause. Compensating cloud biases in the Australian Community Climate and Earth System Simulator (ACCESS) – Atmosphere-only model version 2 (AM2) over the SO were analyzed by \citeA{fiddes2022} and \citeA{fiddes2024}. \citeA{possner2022} showed that over the SO, the DYAMOND GSRM ICON underestimates low-level cloud fraction on the order of 30\% [relative to Moderate Resolution Imaging Spectroradiometer (MODIS) data] and overestimates downwelling TOA SW radiation by approximately 10 Wm$^\mathrm{-2}$ [relative to the Clouds and the Earth’s Radiant Energy System (CERES) data] in the highest model resolution run (2.5 km). \citeA{zhao2022} reported a similar SW radiation bias in five analyzed CMIP6 models over high-latitude SO and the total cloud fraction underestimation on the order of 10\% over the entire 40--60°S SO. Recently, \citeA{ramadoss2024} analyzed 48 hours of km-scale ICON limited-area model NWP simulations over a SO region adjacent to Tasmania against the Clouds, Aerosols, Precipitation, Radiation, and atmospherIc Composition Over the southeRn oceaN (CAPRICORN) voyage cloud and precipitation observations \citeA{mcfarquhar2021}. They found the ICON cloud optical thickness was underestimated relative to Himawari‐8 satellite observations but also identified large differences in cloud top phase.

@@

\begin{figure}[b!]
\centering
\includegraphics[width=\textwidth]{img/ann.pdf}
\caption{
Artificial neural network (ANN) for prediction of precipitation in lidar backscatter. \textbf{(a)} Diagram showing the TensorFlow structure of the ANN, \textbf{(b)} randomly selected example samples of near-surface backscatter in four categories (clear, fog, rain, and snow), as determined by coincident human-performed weather observations, \textbf{(c)} receiver operating characteristic diagram of the ANN, \textbf{(d)} examples of 10-day time series of human-observed (``HUM'') and predicted precipitation based on an ANN trained on all voyages (``ANN'') and all voyages except for the shown voyage (``ANN2'') during three randomly selected voyages with the available data. Here, by ``randomly selected'', we mean selected from the top of a permutation generated by a pseudo-random number generator to prevent authors' bias in the selection.
}
\label{fig:ann}
\end{figure}
